\tool: Programmable, Efficient, and Scalable Secure Two-Party Computation

### 2017-10-28 OaklandSubmission/intro.tex
minor

Secure Two-party Computation (\mpc)~(\cite{yao,gmw}) is a powerful
cryptographic technique that allows two mutually distrusting parties
to compute a joint function of their secret inputs in a way that both
the parties learn nothing about the inputs of each other beyond what
is revealed by their (possibly different) outputs. For example, \mpc
can be used for {\em secure
prediction}~(\cite{shafindss,wu,barni,minionn,secureml}),
where one party (the server) holds a proprietary classifier to predict
a label (e.g. a disease, genomics, or spam detection), and the other
party (the client) holds a private input that it wants to run the
classifier on. Using \mpc guarantees that the server learns nothing
about the client's input or output, and that the client learns nothing
about the server model, beyond what is revelaed by the output
label.

@@

\subsubsection*{Ease of programming} \tool source programs are ideal
functionalities that describe ``what'' computation needs to be done,
rather than ``how'' to do it. In particular, the programmer writes the
high-level computation without thinking about the underlying
cryptographic details. For example, Figure~\ref{fig:ex-sml}
shows an \tool source
program for $w^Tx >b$.
%
%\vspace{0.2cm}
%
%\vspace{0.2cm}
The program is quite similar to what a programmer might
write in C++ or Java. The simplicity of the
language comes with its usual benefits: it is easily accessible to the
developers, there are fewer avenues for making mistakes, developers
don't bear the burden of getting cryptographic details right, and it
is easy to maintain and modify the programs. Needless to say,
frameworks that expose low-level circuit APIs to the programmer do not
enjoy these benefits.

>>>>

Secure Two-party Computation (\mpc)~(\cite{yao,gmw}) is a powerful
cryptographic technique that allows two mutually distrusting parties
to compute a publicly known joint function of their secret inputs in a way that both
the parties learn nothing about the inputs of each other beyond what
is revealed by their (possibly different) outputs. For example, \mpc
can be used for {\em secure
prediction}~(\cite{shafindss,wu,barni,minionn,secureml}),
where one party (the server) holds a proprietary classifier to predict
a label (e.g. a disease, genomics, or spam detection), and the other
party (the client) holds a private input that it wants to run the
classifier on. Using \mpc guarantees that the server learns nothing
about the client's input or output, and that the client learns nothing
about the server model, beyond what is revelaed by the output
label.

@@

\subsubsection*{Ease of programming} \tool source programs are ideal
functionalities that describe ``what'' computation needs to be done,
rather than ``how'' to do it. In particular, the programmer writes the
high-level computation without thinking about the underlying
cryptographic details. For example, Figure~\ref{fig:ex-sml}
shows an \tool source
program for $w^Tx >b$.
%
%\vspace{0.2cm}
%
%\vspace{0.2cm}
The program is quite similar to what a programmer might
write in C++ or Java. The simplicity of the
language comes with its usual benefits: it is easily accessible to the
developers, there are fewer avenues for making mistakes, developers
don't bear the burden of getting cryptographic details right, 
code optimizations can be left to the compiler,
and it
is easy to maintain and modify the programs. Needless to say,
frameworks that expose low-level circuit APIs to the programmer do not
enjoy these benefits.

### 2017-10-28 OaklandSubmission/main.tex
minor

\maketitle
% \begin{abstract}
% The abstract goes here.
% \end{abstract}
\IEEEpeerreviewmaketitle

>>>>

\maketitle
\begin{abstract}
Secure two-party computation (\mpc) allows two mutually distrusting parties to compute any function on their joint inputs, without revealing anything other than the output of the function to one another. %While the application and potential impact of secure computation is virtually limitless, writing an efficient and scalable secure protocol is by no means an easy feat.
 Prior work in designing such protocols, suffered from either a) a lack of programmability (e.g. requiring the programmer to write cryptography-aware circuits for the computation); b) a lack of efficiency for several natural computations (such as machine learning classification tasks); or c) required cryptographers to design hand-crafted protocols for various applications. In this work, we present \tool: a new ``cryptographic-cost aware'' \mpc framework that generates efficient and scalable \mpc protocols from high-level programs that 
%contain absolutely no cryptographic details. Programs in our language 
are easy-to-write, with lines of code that are comparable to their insecure implementations. Furthermore, the \mpc protocols generated by our framework match or outperform recent works that provide hand-crafted \mpc protocols for various functionalities such as classification and matrix factorization (up to a 19x factor!).
\end{abstract}
\IEEEpeerreviewmaketitle
